---
title: "Jupyter Project"
author: "Hamed Diomande"
date: '2023-01-21'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# My Jupyter Notebook on IBM Watson Studio

**Hamed DIOMANDE**

I graduated with a master in Mathematics and Statistics from the University of Ottawa and in the long term I want to become a data analyst in the financial industry like a banks and insurances or in businesses that provides services for the well being of others like Uber, Netflix, Amazon, etc.

*I am interested in data science because I love the process of translating data into a story. Like using storytelling to generate insight and from these insights being able to make strategic choices to resolve problems or provide values to a company or an institution*

### The following code will generate 3 random numbers from a uniform distribution of range [5,10 ]

```{r}
runif(3, min=5, max=10)
```
Information on me:

* Family Name: Diomande 
- First name: Hamed
+ Age: 24
